PANCHANGE_data_preprocessing

### 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed NAs

ramp.ess.raw.id <- ramp.ess.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past = ess.felt_excessively_sleepy_day,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour = ess.break_hour_passenger_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic#,
#         ess.insomnia, # questions are not asked in RAMP
#         ess.narcolepsy,
#         ess.rem_sleep_behaviour_disorder,
#         ess.restless_legs_syndrome,
#         ess.sleep_apnea,
#         ess.sleep_terrors,
#         ess.sleepwalking,
#         ess.other,
#         ess.none  
         ) %>%
  add_column(
    ess.insomnia = NA_real_,
    ess.narcolepsy = NA_real_,
    ess.rem_sleep_behaviour_disorder = NA_real_,
    ess.restless_legs_syndrome = NA_real_,
    ess.sleep_apnea = NA_real_,
    ess.sleep_terrors = NA_real_,
    ess.sleepwalking = NA_real_,
    ess.other = NA_real_,
    ess.none = NA_real_
    ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

ramp.ess.raw.id <- ramp.ess.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         ess.felt_excessively_sleepy_past = ess.felt_excessively_sleepy_day,
         ess.sitting_and_reading,
         ess.watching_tv,
         ess.sitting_inactive_in_a_public_place,
         ess.break_passenger_car_hour = ess.break_hour_passenger_car,
         ess.afternoon_rest_circumstances_lying,
         ess.sitting_and_talking_to_someone,
         ess.sitting_quietly_after_a_lunch_without_alcohol,
         ess.car_minutes_stopped_traffic#,
#         ess.insomnia, # questions are not asked in RAMP
#         ess.narcolepsy,
#         ess.rem_sleep_behaviour_disorder,
#         ess.restless_legs_syndrome,
#         ess.sleep_apnea,
#         ess.sleep_terrors,
#         ess.sleepwalking,
#         ess.other,
#         ess.none  
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
    add_column(
    ess.insomnia = NA_character_,
    ess.narcolepsy = NA_character_,
    ess.rem_sleep_behaviour_disorder = NA_character_,
    ess.restless_legs_syndrome = NA_character_,
    ess.sleep_apnea = NA_character_,
    ess.sleep_terrors = NA_character_,
    ess.sleepwalking = NA_character_,
    ess.other = NA_character_,
    ess.none = NA_character_,
    ess.insomnia_numeric = NA_real_,
    ess.narcolepsy_numeric = NA_real_,
    ess.rem_sleep_behaviour_disorder_numeric = NA_real_,
    ess.restless_legs_syndrome_numeric = NA_real_,
    ess.sleep_apnea_numeric = NA_real_,
    ess.sleep_terrors_numeric = NA_real_,
    ess.sleepwalking_numeric = NA_real_,
    ess.other_numeric = NA_real_,
    ess.none_numeric = NA_real_
    ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
